---
title: "Homework 4"
output: html_notebook
---

| Homework 4                     |                Data Analysis with R |
| :---                           |                                ---: |
| Due by 11:59 PM on Wed Sep 20  | Business Analytics Graduate Program |
| Submit via codePost            |                 BAIS:6060 Fall 2023 |

# Instructions

This homework covers Module 4. Refer to the corresponding materials and
ICE (with solutions) posted on ICON.

Follow all of the guidelines given on prior homeworks, referring to
them as necessary. Here are some important reminders:

- include the required `library(...)` commands in your notebook;

- for this assignment, be sure to use `qplot(...)` instead of `plot(...)`.

- while we used `log` in our module examples, in general only use `log`
when you have a good reason to do so (e.g., correcting the shape of a
histogram); I will indicate when to do this.

**Big Hint!** The exercises below ask you to save your outputs to PNGs
files. In general, get into the habit of first exporting your graphic
with `ggsave(...)` *before* checking to see if the graphic looks correct.
The plot within an R notebook will look sometimes different than the final 
output file, and yet the output file should be considered the final version
(since, for example, it could be added to a report). 

Note, on ##1 the focus is on different types of graphs, not complete
well-formatted graphs. In fact, you will see some overlap of values and
numbers left in Scientific format. While ##2 the focus is on creating a 
complete, good quality data visualization. When you do the class project, 
your graphs should follow this example, although they may not be as complex,
depending upon your analysis.

# Exercises

```{r}

# Load libraries.
library(readr)
library(forcats)
suppressPackageStartupMessages(library(dplyr))

library(ggplot2)
library(scales)

```

Carefully review the included files `movies.txt` and
`movies_transformed.csv` and then execute the following code to load the
CSV file, which matches the solution of the previous homework. Then
complete the exercises below:

```{r}

my_col_types <- cols(
    OpeningDate = col_date(),
    Title = col_character(),
    Studio = readr::col_factor(), # "readr::" prefix avoids conflict with scales
    OpeningGross = col_integer(),
    OpeningTheaters = col_integer(),
    TotalGross = col_integer(),
    TotalTheaters = col_integer(),
    GrossRatio = col_double(),
    Stamina = readr::col_factor() # "readr::" prefix avoids conflict with scales
)
df <- read_csv("movies_transformed.csv", col_types = my_col_types)
new_levels <- levels(df$Studio)
new_levels <- setdiff(new_levels, "Other")
new_levels <- sort(new_levels)
new_levels <- c(new_levels, "Other")
df <- mutate(df, Studio = fct_relevel(Studio, new_levels))

```

## #1

Complete the following *without* changing the contents of `df`.

### (a)

Create a graphic based on a single integer/numeric/double column
of data. (Do not use two or more columns to build this graphic.) Use
GrossRatio as a natural log. Export the graphic to a PNG file named
`1a.png` via the `ggsave(...)` command with options width of 6 inches, 
height of 4 inches, and dpi of 600 pixels.

```{r}



```

### (b)

Create a bar graph based on a single factor column of data. (Do
not use two or more columns to build this graphic.) Use the Studio
column. Export the graphic to a PNG file named `1b.png` via the 
`ggsave(...)` command with options width of 6 inches, 
height of 4 inches, and dpi of 600 pixels.

```{r}



```

### (c)

Create a scatter plot based on exactly two integer/numeric/double 
columns of data. (Do not use three or more columns to build this 
graphic.) Use OpeningGross and TotalGross as the columns. Export 
the graphic to a PNG file named `1c.png` via the `ggsave(...)` 
command with options width of 6 inches, height of 4 inches, and dpi 
of 600 pixels.

```{r}



```

### (d)

Create a heatmap based on exactly two integer/numeric/double
columns of data. (Do not use three or more columns to build this
graphic.) Use TotalTheaters and GrossRatio as the columns. Export 
the graphic to a PNG file named `1d.png` via the `ggsave(...)` 
command with options width of 6 inches, height of 4 inches, and dpi 
of 600 pixels.

```{r}



```

### (e)

Create boxplots of an integer/numeric/double column on a log
scale against a factor column. Use Stamina and OpeningGross as the
columns. Export the graphic to a PNG file named `1e.png` via the 
`ggsave(...)` command with options width of 6 inches, height of 4 
inches, and dpi of 600 pixels.

```{r}



```

### (f)

Use faceting to create a graphic involving exactly two factor
columns. (Do not use three or more columns to build this graphic.) Stamina
column levels should be the column groups on the graph. Export the graphic 
to a PNG file named `1f.png` via the `ggsave(...)` command with options width 
of 6 inches, height of 4 inches, and dpi of 600 pixels.

```{r}



```

## #2

Without changing the contents of df, create a graphic involving three
or more columns of data. "Total Gross Sales" should be on the vertical
axis, "Number of Theaters on Opening Weekend" on the horizontal axis, and
the title should be "Not All Blockbusters Have Staying Power". Then the
legend should be "Staying Power" with values of Stronger, Strong, Weaker,
and Weak. To help in auto-grading, the small value label on the vertical
axis should be $100,000 and the high value should be $1,000,000,000. Then
on the horizontal axis the small value should be 0 and the high value
should be 4000. Also, please adhere to the following rules. These should
always be followed to produce high quality data visualizations.

- Produce the graphic with the following audience in mind: a colleague,
friend, or family member who is familiar with movies and who has
experience reading and understanding graphics of various types, e.g.,
boxplots in a trade magazine. (Your classmates or the professor---people
who are looking at the data to the same level of detail---are *not* the
target audience.)

- Give the graphic a main title, which helps explain the graphic. Here
are some example titles: "Number of Movies Per Studio" and "Gross Ticket
Sales Versus Number of Theaters".

- Relabel axis titles and legend titles so that they are readable and
understandable.

- Relabel the numbers on axes so that they are readable and
understandable, e.g., avoid scientific notation and use "$" for dollar
amounts.

- Make sure no text is accidentally cut out of the graphic. Also make
sure text does not overlap.

- Export the graphic to a PNG file named `2.png` via the `ggsave(...)`
command with option `dpi=600`. Also use options `width=7` and `height=4`.
Default is width of 6 and height of 4, but I am deviating from these 
defaults to allow for the legend and better visual appeal. (Making
the graphic easier to read and understand is a good reason to deviate.)

```{r}

# Create initial plot with 3 columns of data, transparency of 40%, and
# main and x titles



# Update y axis



# Update size legend, using scale_color_hue function



# Change font characteristics of titles, use size 16 with bold format



# Save plot with name 2.png



```
